A sample computation

### 2024-10-03 draft_systoles.tex
Add explicit integer lifts
minor corrections

Now, consider the natural embeddings
\[
i_1: \SL \embeds {\mathbf{SL}_3(\mathbb{R})}
, \] 
\[
i_2: \SL \embeds {\mathbf{SL}_3(\mathbb{F}_2)}
.\]

\begin{Prop}
The pullback 
\[
i_1^* \oplus i_2^*: 
H^2(B\mathbf{SL}_3(\mathbb{R}), \mathbb{Z}/ 2 \mathbb{Z}) \oplus
H^2(B\mathbf{SL}_3(\mathbb{F}_2), \mathbb{Z}/ 2 \mathbb{Z}) \cong (\mathbb{Z} / 2 \mathbb{Z})^2 \to 
H^2(\SL, \mathbb{Z}/ 2 \mathbb{Z}) \cong (\mathbb{Z}/2\mathbb{Z})^{2}
\] 
is an isomorphism.
\end{Prop}

@@

Define $D_1' = 
\left( \begin{smallmatrix}0&6\\1&0\end{smallmatrix}\right) 
, D_2' =
\left( \begin{smallmatrix}2&3\\3&5\end{smallmatrix}\right)
\in \mathbf{SL}_2(\mathbb{F}_7)$.
Project the matrices to 
$\in \mathbf{PSL}_2(\mathbb{F}_7) \cong \in \mathbf{SL}_3(\mathbb{F}_2) $.
Pick a pair of lifts $D_1, D_2 \in \mathbf{SL}_3(\mathbb{Z})$.

@@

Thus we have showed that $E_1, E_2$ have the right characteristic classes and we are done.
\end{proof}
\begin{proof}[Proof of the Theorem \ref{thm_push_homology_vanishes}]
By Lemma \ref{lemma_push_vanishes_iff_pull_vanishes} we shall show that the pullback map in second $\mathbb{Z}/ 2 \mathbb{Z}$-cohomology vanishes.

>>>>

Now, consider the natural mappings
\[
i: \SL \embeds {\mathbf{SL}_3(\mathbb{R})}
, \] 
\[
\pi: \SL \embeds {\mathbf{SL}_3(\mathbb{F}_2)}
.\]

\begin{Prop}
The pullback 
\[
i^* \oplus \pi^*: 
H^2(B\mathbf{SL}_3(\mathbb{R}), \mathbb{Z}/ 2 \mathbb{Z}) \oplus
H^2(B\mathbf{SL}_3(\mathbb{F}_2), \mathbb{Z}/ 2 \mathbb{Z}) \cong (\mathbb{Z} / 2 \mathbb{Z})^2 \to 
H^2(\SL, \mathbb{Z}/ 2 \mathbb{Z}) \cong (\mathbb{Z}/2\mathbb{Z})^{2}
\] 
is an isomorphism.
\end{Prop}

@@

Define $D_1' = 
\left( \begin{smallmatrix}0&6\\1&0\end{smallmatrix}\right) 
, D_2' =
\left( \begin{smallmatrix}2&3\\3&5\end{smallmatrix}\right)
\in \mathbf{SL}_2(\mathbb{F}_7)$.
Project the matrices to 
$\in \mathbf{PSL}_2(\mathbb{F}_7) \cong \in \mathbf{SL}_3(\mathbb{F}_2) $.
Pick a pair of commuting lifts $D_1, D_2 \in \mathbf{SL}_3(\mathbb{Z})$.
One can take them to be 
\begin{equation}
D_1 = 
\begin{pmatrix}
1 & 1 & 0 \\
0 & 1 & 0 \\
0 & 1 & 1
\end{pmatrix}, 
D_2 =
\begin{pmatrix}
1 & 0 & 0 \\
0 & 1 & 0 \\
0 & 1 & 1
\end{pmatrix}
.\end{equation}

@@

Thus we have showed that $E_1, E_2$ have the right characteristic classes and we are done.
\end{proof}
\begin{proof}[Proof of the Theorem \ref{thm_push_homology_vanishes}]
In view of the Lemma \ref{lemma_push_vanishes_iff_pull_vanishes} we shall show that the pullback map in second $\mathbb{Z}/ 2 \mathbb{Z}$-cohomology vanishes.
